A Bidirected String Graph Model of Genome Assembly

### 2012-12-04 presentation/presentation.tex
update slid

\usepackage{graphicx}
\usepackage{listings}
\usepackage{comment}
\usepackage{float}
\usepackage{tikz}
\usepackage{algorithm}
\usepackage[noend]{algorithmic}
\usepackage{multicol}
\usepackage{grffile}

@@

\begin{frame}{Walking through the bidirected string graph (cont.)}
	\vspace{-0.7cm}
	\begin{center}
		\begin{tabular}{p{3.4cm}c}
			\vspace{-0.4cm}
			{\small a.) A bidirected string graph fragment} &
			\begin{tikzpicture}[>=triangle 45,scale=1.5]
				\tikzstyle{every node} = [circle,fill=blue!20,draw=black];
				\node (f) at (0, 0) {f};
				\node (g) at (1.7, 0) {g};
				\draw[>->,style=very thick] (f) edge (g);
			\end{tikzpicture}
			\\
			\vspace{-1.5cm}
			{\small b.) The corresponding overlap (labeled)} &
			\begin{tikzpicture}[>=\ReadArrowType,scale=0.8]
				\draw[->,very thick] (0, 0) node[anchor=east] {$f.B$}
						-> (4, 0) node[anchor=west] {$f.E$};
				\draw[->,very thick] (2, -0.7) node[anchor=east] {$g.B$}
						-> (6, -0.7) node[anchor=west] {$g.E$};
				\draw (2, -1.05) node[anchor=north] {$o.g_{begin}$}
						-- (2, 0.35) node[anchor=south] {$o.f_{begin}$};
				\draw (4, -1.05) node[anchor=north] {$o.g_{end}$}
						-- (4, 0.35) node[anchor=south] {$o.f_{end}$};
			\end{tikzpicture}
		\end{tabular}
	\end{center}
	\begin{tabular}{c|c}
		walk & interpretation \\ \hline
		$f \to g$ & $f.E \to g.E$ with sequence $g[o.g_{end} + 1 \dots ${\tt
		length}$(g)]$ \\
		$g \to f$ & $g.B \to f.B$ with sequence $f[o.g_{begin} - 1 \dots 0]$ \\
	\end{tabular}
	\vspace{0.5cm}
	\begin{itemize}
		\item If we take {\bf each end} of {\bf each read} as a vertex, we can
		make a directed graph equivalent to the bidirected graph.
	\end{itemize}
\end{frame}

>>>>

\usepackage{graphicx}
\usepackage{listings}
\usepackage{comment}
\usepackage{float}
\usepackage{tikz}
\usepackage{algorithm}
\usepackage[noend]{algorithmic}
\usepackage{multicol}
\usepackage{grffile}
%\usepackage[dvips]{graphics}

@@

\begin{frame}{Walking through the bidirected string graph (cont.)}
	\begin{center}
		\vspace{-1cm}
		\begin{tabular}{p{3.6cm}c}
			\vspace{-1.5cm}
			{\small a.) A bidirected string graph fragment} &
			\begin{tikzpicture}[>=triangle 45,scale=1.5]
				\node[circle,fill=blue!20,draw=black] (f) at (0, 0) {f};
				\node[circle,fill=blue!20,draw=black] (g) at (2.0, 0) {g};
				\draw[>->,style=very thick] (f) edge (g);
				\draw (1.00, 0.1) node[anchor=south] {\small \tt TTAGAAGTA};
				\draw (1.00, -0.1) node[anchor=north] {
						\rotatebox{180}{\small \tt
						TGTGTAATC}};
				\draw[->] (0.5, 0.5) ..
					controls (0.7, 0.7) and (1.3, 0.7) ..
					(1.5, 0.5);
				\draw[->] (1.5, -0.5) ..
					controls (1.3, -0.7) and (0.7, -0.7) ..
					(0.5, -0.5);
			\end{tikzpicture}
			\\ \hline
			\vspace{-2.3cm}
			{\small b.) The corresponding overlap (labeled)
			%sequence
			%of overlapped region arbitrary as it is not known purely
			%from the graph fragment)
			} &
			\begin{tikzpicture}[>=\ReadArrowType,scale=0.8]
				\draw[->,very thick] (0, 0) node[anchor=east] {$f.B$}
						-> (4, 0) node[anchor=west] {$f.E$};
				\draw[->,very thick] (2.09, -0.9) node[anchor=east] {$g.B$}
						-> (6.09, -0.9) node[anchor=west] {$g.E$};

				\draw (0, -0.1) node[anchor=south west]
					{\hspace*{-1.4mm}{\small \tt
						%GATTACACAGTGTAGTT
						GATTACACA\hspace*{0.1cm}$a_1 \dots a_n$
					}};

				\draw (0, 0.1) node[anchor=north west]
					{\hspace*{-2.6mm}
						\rotatebox{180}{{\small \tt TGTGTAATC}}};

				\draw (2.09, -1.0) node[anchor=south west]
					{\hspace*{-1.4mm}{\small \tt
						%GTGTAGTTTTAGAAGTA
						\hspace*{0.1cm}$a_1 \dots a_n$\hspace*{0.25cm}TTAGAAGTA
					}};

				\draw (2.09, -0.9) node[anchor=north west]
					{\hspace*{12.48mm}
						\rotatebox{180}{{\small \tt TACTTCTAA}}};

				\draw (2.09, -1.4) node[anchor=north] {$o.g_{begin}$}
						-- (2.09, 0.6) node[anchor=south] {$o.f_{begin}$};
				\draw (3.99, -1.4) node[anchor=north] {$o.g_{end}$}
						-- (3.99, 0.6) node[anchor=south] {$o.f_{end}$};
			\end{tikzpicture}
		\end{tabular}
	\end{center}
	\begin{tabular}{c|c}
		walk & interpretation \\ \hline
		$f \to g$ & $f.E \to g.E$ with sequence $g[o.g_{end} + 1 \dots ${\tt
		length}$(g)]$ \\
		$g \to f$ & $g.B \to f.B$ with sequence $f[o.g_{begin} - 1 \dots 0]$ \\
	\end{tabular}
	%\vspace{0.5cm}
	%\begin{itemize}
		%\item If we take {\bf each end} of {\bf each read} as a vertex, we can
		%make a directed graph equivalent to the bidirected graph.
	%\end{itemize}
\end{frame}
